\section{User manual}
\subsection{How to run}
First, either Ganache or \mintinline{bash}{truffle develop} is required. The
\mintinline{bash}{start_ganache.sh} script contains the private keys used
during development by Ganache. This allows to avoid having to import new keys
at every Ganache restart. Feel free to use the script, or to use your own keys.

After starting a local blockchain instance, run \mintinline{bash}{npm ci} and
\mintinline{bash}{truffle migrate} to download OpenZeppelin dependencies and
deploy contracts.

Finally, run \mintinline{bash}{npm ci} and \mintinline{bash}{npm start} in the
\mintinline{bash}{frontend} folder. This will download dependencies for the
frontend and start the React development server.

\subsection{Demo}
Tests that simulate a game are available inside
\mintinline{bash}{test/test_battleshipGame.js}. Tests were development mainly
to validate that changes to the contract implementation were not breaking
contract interaction.

To manually play battleship, two browsers are needed (Metamask inside an
incognito browser window should also work). The following assumes that keys and
network are already setup for Ganache or \mintinline{bash}{truffle develop}.

First, navigate on both browsers to
\href{http://localhost:8080}{\color{blue}http://localhost:8080}. The user
interface should provide enough guidance for playing a battleship game. A
couple of notes:
\begin{itemize}
	\item By default, 10 ships must be placed, making it time-consuming to play a full
	      game. It is possible to change the number of required ships by changing
	      \mintinline{solidity}{SHIP_CELLS_BOARD} in
	      \mintinline{bash}{BattleshipGame.sol:27}. Note that, with a value different
	      from 10, tests will fail, and UI will not update the ship requirements shown as
	      an aid to the player in the \mintinline{bash}{/game/:address/placing} page.
	\item Events emitted by the contract drive the UI updates. Events delivery is
	      sometimes delayed by several seconds. Be patient, the UI will eventually update
	      when the event is received.
	\item It may rarely occur that data fetching from the contract happens too early. In
	      the case something odd happens, reloading the page will most likely fix it.
\end{itemize}

Steps for playing (assuming two different accounts are being used on two
different browsers):
\begin{enumerate}
	\item Create a game
	\item Either join a random game, or join it using the game ID shown in the first
	      browser
	\item Place a bet with the first user
	\item Accept it with the second user
	\item Place the required ships (10, unless \mintinline{bash}{BattleshipGame.sol:27}
	      has been modified) on both boards
	\item Commit the board
	\item Take turns shooting at the opponent's board by clicking on the
	      \mintinline{bash}{shoot} HTML button
	\item When one of the player's reaches the number of sunk ships set, the winner will
	      be declared
	\item Then winner has to send its board for verification by clicking on the
	      \mintinline{bat}{Send board for verification} button
	\item If placement was legitimate, the winner will be able to click a
	      \mintinline{bat}{withdraw} button to transfer the wager to its account.
	      Otherwise, the opponent will be declared winner and redirected to the
	      withdrawal page.
\end{enumerate}

